\MakeAbstract{
渗透测试通过模拟攻击者行为来发现系统漏洞，是Web安全防护中不可缺少的环节。随着大语言模型（LLM）推理能力的增强，已有多项工作尝试用LLM Agent来实现渗透测试的自动化。AutoPT是其中比较有代表性的一个，它用渗透测试状态机（PSM）对测试流程建模，约束了Agent的决策空间，但在实际使用中仍受限于状态转移粒度较粗、缺少浏览器交互工具以及只有命令行界面等问题。

本文针对这三个问题改进了AutoPT。我们设计了一套ReAct提示词模板由所有Agent共用，但各自有不同的角色边界。同时将AutoPT 的Scan阶段拆分为端口发现、服务知识匹配、漏洞扫描和结果评估四个子阶段，配合上下文压缩、PoC容错提取和Check结果匹配收窄等机制。为了加强对不同漏洞的自适应能力，我们新增了三个浏览器扩展工具用于表单交互，ReAct解析器也改造为多级容错机制。此外还搭建了一套基于Flask和JavaScript的Web Console管理界面。

实验使用了与原论文相同的20个CVE漏洞环境和三种模型，共进行300次独立测试。改进版总成功率为63.67\%，比原版高出约39\%；原版60组测试中有38组实验成功率为0\%，改进版压缩到了3组。弱模型GPT-3.5-turbo的变化最为突出，成功率从原版的约7\%跃升至54\%。同样以原论文中表现最好的GPT-4o-mini来计算成本，改进版单次成本降低69\%，平均耗时缩短42\%。这些数据说明，在不更换更强模型的前提下，对PSM架构内的流程控制和工具能力做针对性改进，就足以带来成功率和成本上的明显改善。
}{自动化渗透测试，大语言模型，智能体，渗透测试状态机，ReAct框架}

\MakeAbstractEng{
The main thing in this paper is about penetration testing, that is to find vulnerabilities in the system by pretending to be a hacker. Now with the large language model LLM, you can make programs that can automate this process, such as AutoPT is one of the best. It uses something called a penetration state machine PSM to manage the testing process so that the program doesn’t run away. However, it was actually found that the state of AutoPT was not thin enough to operate the web interface well, so it can only be run with the command line.

This paper reworks AutoPT on all three fronts. A shared ReAct prompt template gives every agent the same output format while assigning each one a distinct role. Scan is no longer a single monolithic step; it now goes through port discovery, service knowledge matching, vulnerability scanning, and result evaluation in sequence. Context compression keeps token usage from blowing up across ReAct iterations, a four-level fallback extracts usable PoC even when the Inquire agent's output is malformed, and the Check phase only looks at real tool output when deciding success or failure. Three new browser tools (fill\_element, select\_option, wait\_for\_selector) handle form-based interactions that the original Playwright toolkit could not, and the ReAct parser has been rebuilt to tolerate the kind of format deviations that chain-of-thought models tend to produce. A Flask + vanilla JavaScript Web Console replaces the command-line interface.

We ran 300 independent tests (20 real CVE environments $\times$ 3 models $\times$ 5 runs each), using exactly the same setup as the original AutoPT paper. Overall success rate went from roughly 25\% to 63.67\%. Out of 60 model-vulnerability combinations that scored 0\% before, only 3 still do. GPT-3.5-turbo saw the biggest jump, going from around 7\% to 54\% --- same model, different architecture. On cost, GPT-4o-mini (the best model in the original paper) now costs 69\% less per test and finishes 42\% faster. None of this required a more powerful model; the gains came from tightening process control, expanding the tool set, and making the system easier to operate.
}{automated penetration testing, large language model, agent, penetration state machine, ReAct framework}
